---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# atlantisdrive

<!-- badges: start -->
<!-- badges: end -->

Tools for moving Atlantis files to and from google drive

## Installation

``` r
remotes::install_github("andybeet/atlantisdrive",build_vignettes = TRUE)
```

## Usage


```{r}
library(atlantisdrive)
```

To view the list of folders under the root folder on google drive. The id of the root folder is lazily loaded with `atlantisdrive` and used as the default argument

```{r}
get_dirs()
```


To view the content of one of these folders:

```{r}
get_files(targetDir = "Development")
```

To pull files from this folder to your local machine (Note: partial matches to file names are allowed)

```{r, eval = FALSE}
pull_from_drive(localPath=here::here(),fileList="ATLNT",googledriveFolder="Development")
```

To push files from your current working directory to google drive (Note: partial matches to file names are allowed). Push to "Development" folder on google drive

```{r, eval = FALSE}
push_to_drive(id=NULL, localPath=here::here(), fileList=NULL, googledriveFolder="Development", rootid=atlantisdrive::rootid, overwrite = TRUE)
```

Note: special case when `fileList = NULL`. All Atlantis core files are pushed.

To list all Atlantis core files that currently reside in your working directory

```{r}
list_core_files(path=here::here())
```

To list all files (from scenario "ATLNTS-1") required for atlantisom. 

```{r}
list_atlantisom_files(scenario="ATLNTS-1")
```
