---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# atlantisdrive

<!-- badges: start -->
![deploy to github pages](https://github.com/andybeet/atlantisdrive/workflows/deploy%20to%20github%20pages/badge.svg)
<!-- badges: end -->

Tools for moving Atlantis files to and from Google drive

## Installation

``` r
remotes::install_github("andybeet/atlantisdrive")
```

## Usage

```{r}
library(atlantisdrive)
```

To view the list of files/folders under the root folder (as defined by `id`) on Google drive use

```{r, echo=T, eval = F}
get_file_list()
get_file_list(targetDir = "Development")
get_file_list(targetDir = "Development/Example")
```

To pull all files containing the string "ATLNT" from the "Development" folder to your local machine (Note: partial matches to file names are allowed)

```{r, echo = T, eval = F}
pull_from_drive(localPath=here::here(),fileList="ATLNT",googledriveFolder="Development")
```

To push all files from your "output" folder in your current working directory to the "Testing/Example" folder on Google drive (Note: partial matches to file names are allowed). All files are overwritten.

```{r, echo = T, eval = F}
push_to_drive(id=NULL, localPath=here::here("output"), fileList=NULL, googledriveFolder="Testing/Example", rootid=atlantisdrive::rootid, overwrite = TRUE)
```

Note: special case when `fileList = NULL`. All Atlantis core files are pushed.

To push all files containing the string "xml" from your "output" folder in your current working directory to the "Testing/Example" folder on Google drive. Appends the string "climate" to beginning of all files

```{r, echo=T , eval = F}
push_to_drive(id="climate", localPath=here::here("output"), fileList="xml", googledriveFolder="Testing/Example", rootid=atlantisdrive::rootid, overwrite = TRUE)
```

