---
title: "atlantisdrive"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{atlantisdrive}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(atlantisdrive)
```

The idea behind `atlantisdrive` is to allow a user to select groups of files produced by Atlantis, add a naming convention, and push them to google drive in a systematic way. All the user requires, is the `id` of the root folder on google drive and authentication credentials to access the folder. Google drive then becomes an organized repository for Atlantis output. Others can then use `atlantisdrive` to pull output, after which they can use `atlantisom` and/or `atlantisdiagnostics` to explore the model run output.

## Example

We first run Atlantis (on Linux) using:

``` r
atlantisMerged -i neus_init.nc 0 -o neus_output.nc -r at_run.prm -f at_force_LINUX.prm 
-p at_physics.prm -b at_biology.prm -h at_harvest.prm -e at_economics.prm -s neus_groups.csv
-q neus_fisheries.csv -t . -d outputDir
```

The `neus_itit.nc` file, the `.prm` and `csv` files are input files to the model. The `neus_output.nc` is the name of the main output file and the text string `neus_output` is used as a prefix to many of the output files. `outputDir` is the name or path to the directory where all output will be saved.

A typical run will output core files with the extensions:

1.    txt
1.    ts
1.    xml
1.    nc

All of the "txt" and "nc" files are prefixed with `neus_output` (in general the prefix string is the name of the output file)

We now want to push all of these core files to google drive for archiving and/or sharing with others. We can achieve this in a couple of steps.

1. Define the path to the output on the local machine

For example:

```{r eval = FALSE}
localPath <- here::here("outputFolder")
```

2. Get the names of the core files to push to google drive

```{r eval = FALSE}
coreFiles <- atlantisdrive::list_core_files(localPath)
```

3. Obtain the root id of google drive and authenticate ones self

```{r eval = FALSE}
# this is a ficticious number
rootid <- "23kcfkn3vjk56ivknk44nkcn4985c"
```

4. Push files to google drive

For example, push to `myWork` folder (you will be prompted to create the folder if it doesn't exist)

```{r eval = FALSE}
atlantisdrive::push_to_drive(rootid=rootid,localPath = localPath,googledriveFolder = "myWork")

```


